Train Harder, Smarter:\\Using Graph Theory to Create Route Suggestions

### 2013-11-14 paper.tex
Reorganized the pyroute files and created a preliminary grower.
The grower has a few issues at the moment. Most problematically, it does not
take input for parameters. Additionally, it needs some work to adjust the
parameters to proper units.

The next step is to utilize these equations to calculate $\theta$. At any point
along the algorithm, we are at some $x_i$, and we have travelled a distance,
$d_i$. Figure~\ref{fig:algvals} should help to understand what exactly the
algorithm is attempting to achieve. The idea is this: if we have travelled some
distance $d_i$, then there is an $x_{\mbox{{\tiny ideal}}}$ on the ``ideal''
loop. The arc between $x_{\mbox{{\tiny ideal}}}$ and $x_0$ will be of length
$d_i$. The algorithm searches for a point $x_j$ such that the arc between
$x_{\mbox{{\tiny ideal}}}$ and $x_j$ will have the \emph{same} distance as the
line between $x_i$ and $x_j$. Fortunately, we have framed the equations for
calculating $x_j$ in terms of the distance travelled along the arc, and the
distance between $x_i$ and $x_j$ can easily be calculated using the pythagorean
theorem. Note that we find $x_j$ as follows:
\begin{align}
  x_j.x = \frac{d}{2\pi} ( & \cos( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
                                  + \phi ) \notag \\ & - \cos \phi ) + x_0.x
                                  \label{eq:xjx} \\
  x_j.y = \frac{d}{2\pi} ( & \sin( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
                                  + \phi ) \notag \\ & - \sin \phi ) + x_0.y.
                                  \label{eq:xjy}
\end{align}
To satisfy our constraint, we have
\begin{equation}
  d_j = \sqrt{ ( x_j.x - x_i.x )^2 + ( x_j.y - x_i.y )^2 }. \label{eq:dists}
\end{equation}
Obviously, this is a rather difficult equation to truly solve, so we must only
heuristically find a solution. Luckily, we
have a fairly small search space, since $d - d_i > d_j > 0$. On the other hand,
it is not readily apparent how these solutions will behave. We can, however,
be certain that it is continuous, so we can proceed as follows:
\begin{enumerate}
\item Check if the optimal solution would require that we move around the loop
  again. This will happen if
  \[d_i+\sqrt{(x_0.x-x_i.x)^2+(x_0.y-x_i.y)^2} > d.\]
  In this case, we set $x_j = x_0$, and stop searching.
\item \emph{NEEDS MORE WORK}
\end{enumerate}

>>>>

The next step is to utilize these equations to calculate $\theta$. At any point
along the algorithm, we are at some $x_i$, and we have travelled a distance,
$d_i$. Figure~\ref{fig:algvals} should help to understand what exactly the
algorithm is attempting to achieve. The idea is this: if we have travelled some
distance $d_i$, then there is an $x_{\mbox{{\tiny ideal}}}$ on the ``ideal''
loop. The arc between $x_{\mbox{{\tiny ideal}}}$ and $x_0$ will be of length
$d_i$. The algorithm searches for a point $x_j$ such that the arc between
$x_{\mbox{{\tiny ideal}}}$ and $x_j$ will have the \emph{same} distance as the
line between $x_i$ and $x_j$. Fortunately, we have framed the equations for
calculating $x_j$ in terms of the distance travelled along the arc, and the
distance between $x_i$ and $x_j$ can easily be calculated using the pythagorean
theorem. Note that we find $x_j$ as follows:
\begin{align}
  x_j.x = \frac{d}{2\pi} ( & \cos( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
                                  + \phi ) \notag \\ & - \cos \phi ) + x_0.x
                                  \label{eq:xjx} \\
  x_j.y = \frac{d}{2\pi} ( & \sin( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
                                  + \phi ) \notag \\ & - \sin \phi ) + x_0.y.
                                  \label{eq:xjy}
\end{align}
To satisfy our constraint, we have
\begin{equation}
  d_j = \sqrt{ ( x_j.x - x_i.x )^2 + ( x_j.y - x_i.y )^2 }. \label{eq:dists}
\end{equation}
Obviously, this is a rather difficult equation to truly solve, so we must only
heuristically find a solution. Luckily, we
have a fairly small search space, since $d - d_i > d_j > 0$. On the other hand,
it is not readily apparent how these solutions will behave. We can, however,
be certain that it is continuous, so we can proceed as follows:
\begin{enumerate}
\item Calculate \eqref{eq:xjx} and \eqref{eq:xjy} for all $\{ d_j |
  0 \leq d_j \leq d - d_i \mbox{ and } d_j = n(0.01d), n \in \mathbb{Z} \}$.
\item Calculate \eqref{eq:dists} for each of these values.
\item If the minimal difference between the $d_j$ calculated in \eqref{eq:dists}
  and the $d_j$ provided in \eqref{eq:xjx} and \eqref{eq:xjy} is less than
  10\% of $d$, then use the $x_j$ calculated there.
\item Otherwise, use $x_0$ as $x_j$.
\end{enumerate}
